\huge Tor's Usability for Censorship Circumvention

### 2016-04-23 pets2017-paper/pets2017-paper.tex
More specific.
Move the first cite of "Tor" to the end of the sentence.
So the first sentence can have a little more impact.

Tor~\cite{dingledine2004tor} is an anonymity network that routes traffic through a series of relays
that makes it difficult to observe the source and destination. Tor's anonymizing functionality coincidentally also circumvented censorship. Eventually, censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for that reason~\cite{winter2012great}. Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network indistinguishable, and advanced techniques to resist blocking.

@@

\begin{figure}
\small
\begin{itemize}
\renewcommand{\labelitemi}{$\circ$}
\item Connect with provided bridges\\
Transport type:
\begin{itemize}
\item flashproxy
\item fte
\item fte-ipv6
\item meek-amazon
\item meek-azure
\item meek-google
\item obfs3 (recommended)
\item obfs4
\item scramblesuit
\end{itemize}
\item Enter custom bridges\qquad\fbox{Help}\\
\end{itemize}
\caption{
Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
The obscure strings under ``Connect with provided bridges'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges'', there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines.
}
\label{fig:bridge-options}
\end{figure}

>>>>

Tor is an anonymity network that routes traffic through a series of relays
that makes it difficult to observe the source and destination~\cite{dingledine2004tor}. Tor's anonymizing functionality coincidentally also circumvented censorship. Eventually, censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for that reason~\cite{winter2012great}. Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network indistinguishable, and advanced techniques to resist blocking.

@@

\begin{figure}
\small
\begin{itemize}
\renewcommand{\labelitemi}{$\circ$}
\item Connect with provided bridges\\
Transport type:
\begin{itemize}
\item flashproxy
\item fte
\item fte-ipv6
\item meek-amazon
\item meek-azure
\item meek-google
\item obfs3 (recommended)
\item obfs4
\item scramblesuit
\end{itemize}
\item Enter custom bridges\qquad\fbox{Help}\\
\end{itemize}
\caption{
Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
The obscure strings under ``Transport type'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges'', there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines.
}
\label{fig:bridge-options}
\end{figure}
